RL-Musician: A Tool for Music Composition with Reinforcement Learning

### 2019-10-24 docs/paper/paper.tex
docs: Start describing evaluational rules

\date{September 30, 2019}

@@

Agent takes action by drawing it from probability distribution returned by its actor model. An actor model can be every function that takes observation as input and returns probability distribution over cells from the current time step. Here, shallow neural network is used as actor model. Its weights can be viewed as something that defines transition matrix for a Markov chain from which actions are generated.

@@

>>>>

\date{Ocotber 26, 2019}

@@

Agent takes action by drawing it from probability distribution returned by its actor model. An actor model can be every function that takes observation as input and returns probability distribution over cells from the current time step. Here, shallow neural network is used as actor model. Its weights can be viewed as something that defines transition matrix for a Markov chain from which sequence of piano roll's states is generated.

@@

Eight properties of a final piano roll are evaluated at the current revision of the study.

\begin{itemize}
	\item \textbf{Consonances.} A negative or positive score is granted for each pair of sounding cells from the same column, then all these scores are summed. Each pair-related score depends on interval between the two corresponding pitches. The more consonant the interval is, the higher the score is. However, there is an exception -- score is zero for intervals of integer number of octaves although they are perfectly consonant. This is done in order to prevent doubling the same melody in different lines.
	\item \textbf{Absence of notes not from the specified scale.} Mode (major or minor) and position of a row with the tonic are set by the user before training. A negative penalty is assigned to each sounding cell of a pitch that does not belong to the specified scale.
	\item \textbf{Conjunct motion.} A positive score is granted for every sounding cell such that the previous cell of the same pitch is not sounding, but there is a sounding cell of close enough pitch in the previous column.
	\item \textbf{Contrary motion.} A positive score is granted for every column such that there are both a sounding cell of pitch lower than that of closest to it sounding cell from the previous column and a sounding cell of pitch higher than that of closest to it sounding cell from the previous column.
    \item \textbf{Noncyclicity.} From subject matter point of view, this score penalizes pieces where the same sequence of sound events is repeated over and over again. Technically, it is implemented as  
\end{itemize}
